ShrinkNets: Learning Network Size while Training

### 2018-02-10 paper/ICML/theory.tex
minor fixes

We can prove that under the condition: $\forall j\in \intint{1, p},
\norm{\left(\bm{A}^T\right)_j}_2 = 1$ the two problems are equivalent
(\cref{gps_equivalence}, see Apendix). However if we relax this constraint then \shrink
becomes non-convex and has no global minimum
(\cref{unconstrained_non_convex,unconstrained_shrinknet_no_min}, also in Appendix). Fortunately,
by adding an extra term to the \shrink regularization term we can prove that:
%
\begin{equation}
  \min_{\bm{A}, \bm{\beta}} \norm{\bm{y} - \bm{A}\diag{\bm{\beta}}\bm{x}}_2^2 + \Omega_\lambda^s + \lambda_2\norm{A}_p^p
\end{equation}
%
has global minimums for all $p>0$ (\cref{shrinknet_regularized_minimum}).
This is the reason we defined the regularized \shrink penalty above as:
%
\begin{equation}
  \Omega_{\lambda, \lambda_2, p}^{rs} = \lambda\norm{\bm{\beta}}_1 + \lambda_2\norm{\bm\theta}_p^p
\end{equation}
%
In practice we observed that $p=2$ or $p=1$ are good a choice; note that the latter
will also introduce additional sparsity into the parameters because the $L_1$ is, 
thest best convex approximation of the $L_0$ norm.

>>>>

We can prove that under the condition: $\forall j\in \intint{1, p},
\norm{\left(\bm{A}^T\right)_j}_2 = 1$ the two problems are equivalent
(\cref{gps_equivalence}, see Apendix). However if we relax this constraint then \shrink
becomes non-convex and has no global minimum
(\cref{unconstrained_non_convex,unconstrained_shrinknet_no_min}, also in Appendix). Fortunately,
by adding an extra term to the \shrink regularization term we can prove that:
%
\begin{equation}
  \min_{\bm{A}, \bm{\beta}} \norm{\bm{y} - \bm{A}\diag{\bm{\beta}}\bm{x}}_2^2 + \Omega_\lambda^s + \lambda_2\norm{A}_p^p
\end{equation}
%
has global minimums for all $p>0$ (\cref{shrinknet_regularized_minimum}).
This is the reason we defined the regularized \shrink penalty above as:
%
\begin{equation}
  \Omega_{\lambda, \lambda_2, p}^{rs} = \lambda\norm{\bm{\beta}}_1 + \lambda_2\norm{\bm\theta}_p^p
\end{equation}
%
In practice we observed that $p=2$ or $p=1$ are good a choice; note that the latter
will also introduce additional sparsity into the parameters because the $l_1$ is, 
thest best convex approximation of the $l_0$ norm.
